DOpElib: A Goal Oriented Software Library for Computing PDEs and Optimization Problems

### 2012-05-24 Paper_May_2012/main.tex
Modifications in the paper

\documentclass[twoside, 11pt]{article}
\usepackage{jnm}
%  
\author{Christian\,Goll\footnotemark[1]\comma Thomas\,Wick\footnotemark[1] 
\comma Winnifried\,Wollner\footnotemark[1]\thanks{%
Institut f\"ur Angewandte Mathematik, Universit\"at Heidelberg, Im Neuenheimer Feld 293/294,
			D-69120 Heidelberg, Germany.}
}

\sauthor{C. Goll, T. Wick and  W. Wollner}

\title{DOpE: A Goal Oriented Software Library for Computing PDEs and Optimization Problems}
\stitle{DOpE: A Goal Oriented Software Library}
\received{Received \hfill}
%
%%% User-requested packages placed after this line %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsfonts,amssymb,amsmath}
\usepackage{booktabs,dcolumn}
\usepackage[T1]{fontenc}
\usepackage{mathtools}
\usepackage{enumerate,graphicx}
\usepackage{subfig}
\usepackage{multirow}
% \usepackage[center]{subfigure}
\numberwithin{equation}{section}
\usepackage[noend]{algorithmic}                        %Algorithm typesetting environment
\usepackage[ruled]{algorithm}
\usepackage{braket}                             %Provides \Set for typing sets
\usepackage{color}
\usepackage[square,sort&compress,numbers]{natbib}
\usepackage{float}
\usepackage{subfig}

@@

@@

\abstract{%
In this article, we describe the software library 
package \textit{Deal Optimization Environment} (DOpE).
Its main feature is to give a unified interface to high level algorithms such as 
time stepping methods, nonlinear solvers and optimization routines. The performance and features 
of the software package are demonstrated by computing 
four numerical tests.

}

\keywords{%

}

%
\begin{document}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{introduction}
The \textit{Deal Optimization Environment} (DOpE) project is 
based on the \textit{deal.II} \citep{deal} finite element library which has been developed
 initially by W. Bangerth, R. Hartmann, and G. Kanschat \cite{deal}.
Its main feature is to give a unified interface to high level algorithms such as 
time stepping methods, nonlinear solvers and optimization routines. 
We aim that the user should only need to write those parts
of the code that are problem dependent while all invariant parts of the algorithms
should be reusable without any need for further coding.
In particular, the user should be able to switch between various different 
algorithms without the need to rewrite the problem dependent code, though he or she will
have to replace the algorithm object with an other one.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\bibliographystyle{abbrvnat}
\bibliographystyle{plainnat}
\bibliography{lit}
%

>>>>

\documentclass[prodmode,acmtoms]{acmsmall}
%

% Package to generate and customize Algorithm as per ACM style
\usepackage[ruled]{algorithm2e}
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

% Metadata Information
\acmVolume{0}
\acmNumber{0}
\acmArticle{00}
\acmYear{0000}
\acmMonth{0}

%
%%% User-requested packages placed after this line %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsfonts,amssymb,amsmath}
\usepackage{booktabs,dcolumn}
\usepackage[T1]{fontenc}
\usepackage{mathtools}
\usepackage{enumerate,graphicx}
\usepackage{subfig}
\usepackage{multirow}
% \usepackage[center]{subfigure}
\numberwithin{equation}{section}
\usepackage{braket}                             %Provides \Set for typing sets
\usepackage{float}
\usepackage{subfig}

@@

%
\begin{document}
\markboth{C. Goll, T. Wick, and W. Wollner}{DOpElib: A Goal Oriented Software Library}

\title{DOpElib: A Goal Oriented Software Library for Computing PDEs and Optimization Problems}

\author{CHRISTIAN GOLL
\affil{University of Heidelberg}
THOMAS WICK
\affil{University of Heidelberg}
WINNIFRIED WOLLNER
\affil{University of Hamburg}}

@@

\begin{abstract}
In this article, we describe the software library 
\textit{Deal.II Optimization Environment} (DOpElib).
The main feature of DOpElib is that it provides a unified interface to high level algorithms 
such as time stepping methods, nonlinear solvers and optimization routines. This structure ensures 
that first of all the user is required to write those sections of code that are specific to 
the considered problem. Second, the exchange of parts of the used routines is possible 
with the need for just a few lines of code to change.
The article illustrates performance and features 
of the software package by four numerical tests. 
\end{abstract}

%\category{C.2.2}{Computer-Communication Networks}{Network Protocols}

%\terms{Design, Algorithms, Performance}

%\keywords{Wireless sensor networks, media access control,
%multi-channel, radio interference, time synchronization}

%\acmformat{Zhou, G., Wu, Y., Yan, T., He, T., Huang, C., Stankovic,
%J. A., and Abdelzaher, T. F.  2010. A multifrequency MAC specially
%designed for  wireless sensor network applications.}

\begin{bottomstuff}
Author's adresses: C. Goll {and} T. Wick, Institut f\"ur Angewandte Mathematik, Universit\"at Heidelberg;
W. Wollner, Fachbereich Mathematik, Universit\"at Hamburg.
\end{bottomstuff}

\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{introduction}

The \textit{Deal Optimization Environment} (DOpElib) project is 
based on the \textit{deal.II} \cite{deal} finite element library which has been developed
 initially by W. Bangerth, R. Hartmann, and G. Kanschat \cite{deal}.
Its main feature is to give a unified interface to high level algorithms such as 
time stepping methods, nonlinear solvers and optimization routines. 
We aim that the user should only need to write those parts
of the code that are problem dependent while all invariant parts of the algorithms
should be reusable without any need for further coding.
In particular, the user should be able to switch between various different 
algorithms without the need to rewrite the problem dependent code, though he or she will
have to replace the algorithm object with an other one.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\bibliographystyle{abbrvnat}
\bibliographystyle{acmsmall}
\bibliography{lit}
%
